Redshift Evolution of the Underlying Type Ia Supernova Stretch Distribution

### 2020-12-17 Nicolas.tex
Changed fig. 6 to mean + caption, changed affiliation

\author{
    N. Nicolas \thanks{n.nicolas@ip2i.in2p3.fr, equal contribution} \inst{1} 
    \and M. Rigault \thanks{m.rigault@ip2i.in2p3.fr, equal contribution} \inst{2}
    \orcid{0000-0002-8121-2560}
    \and\\ Y. Copin \inst{1}
    \orcid{0000-0002-5317-7518}
    \and R. Graziani \inst{2}
    \and G. Aldering\inst{3}
    \and M. Briday\inst{1}
    \and Y.-L. Kim\inst{1}
    \orcid{0000-0002-1031-0796}
    \and J. Nordin\inst{4}
    \and Saul Perlmutter\inst{3}
    \and M. Smith\inst{2,5}
    \orcid{0000-0002-3321-1432}
}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.7\linewidth]{Article_figures/stretchevol_all_vs_snf.pdf}
    \caption{Evolution of the mean SN \textsc{\texttt{SALT2.4}} stretch ($x_1$)
        as a function of redshift. Markers show the mean stretch measured in
        redshift bins of equal sample size, indicated in light gray at the
        bottom of each redshift bin. Full and light markers are used when
        considering the fiducial or the conservative samples, respectively. The
        orange horizontal line represents the mean stretch of the fiducial
        sample, illustrating the expectation if the SN stretch distribution is
        not evolving with redshift. Best fits of our Base drifting model are
        shown as blue, dashed-blue and gray, when fitted on the fiducial sample,
        the conservative one or the SNfactory dataset only, respectively; all
        are compatible. The light-blue band illustrates the amplitude of the
        error (incl. covariance) of the best fit model when considering the
        fiducial dataset.}
    \label{fig:modelall}
\end{figure*}

>>>>

\author{
    N. Nicolas \thanks{n.nicolas@ip2i.in2p3.fr, equal contribution} \inst{1} 
    \and M. Rigault \thanks{m.rigault@ip2i.in2p3.fr, equal contribution} \inst{1}
    \orcid{0000-0002-8121-2560}
    \and\\ Y. Copin \inst{1}
    \orcid{0000-0002-5317-7518}
    \and R. Graziani \inst{2}
    \and G. Aldering\inst{3}
    \and M. Briday\inst{1}
    \and Y.-L. Kim\inst{1}
    \orcid{0000-0002-1031-0796}
    \and J. Nordin\inst{4}
    \and Saul Perlmutter\inst{3}
    \and M. Smith\inst{1,5}
    \orcid{0000-0002-3321-1432}
}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.7\linewidth]{Article_figures/stretchevol_all_vs_snf-mean.pdf}
    \caption{Evolution of the mean SN \textsc{\texttt{SALT2.4}} stretch ($x_1$)
        as a function of redshift. Markers show the mean stretch measured in
        redshift bins of equal sample size, indicated in light gray at the
        bottom of each redshift bin. \nn{Individual $x_1$ errors, subdominant cause
        of the total scatter, have not been accounted for when measuring the
    $x_1$ means.} Full and light markers are used when considering the
        fiducial or the conservative samples, respectively. The orange
        horizontal line represents the mean stretch of the fiducial sample,
        illustrating the expectation if the SN stretch distribution is not
        evolving with redshift. Best fits of our Base drifting model are shown
        as blue, dashed-blue and gray, when fitted on the fiducial sample, the
        conservative one or the SNfactory dataset only, respectively; all are
        compatible. The light-blue band illustrates the amplitude of the error
    (incl. covariance) of the best fit model when considering the fiducial
dataset.}
    \label{fig:modelall}
\end{figure*}
